\LARGE \bf Child-Robot Spatial Arrangement in a Learning by Teaching Activity

### 2016-05-24 paper-Ro_Man-2016.tex
start proofreading

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the spatial arrangement of the interaction on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
In this activity, the child teaches a Nao robot how to write by hand.
Typically in a educational child robot interaction, face-to-face spatial arrangements are usually set.
We explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
We estimated the gaze behaviour of the child and the consistency of their grading of the robot with regard to the robot's progress in writing. 
Even-though the demonstrations provided by children were not different between the two conditions (i.e. the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, we present an experiment in the context of a child-robot interaction where we study the influence of the child-robot spatial arrangement on the child's focus of attention and the perception of the robot's performance in the ``''Co-Writer learning by teaching'' activity.
In this activity, the child teaches a Nao robot how to handwrite.
In an educational child robot interaction, face-to-face spatial arrangements are usually set.
We explored two spatial conditions from Kendon's F-formation, the side-by-side and the face-to-face formations in a within subject experiment.
We estimated the gaze behaviour of the child and the consistency of their grading of the robot with regard to the robot's progress in writing. 
Even-though the demonstrations provided by children were not different between the two conditions (i.e. the robot's learning didn't differ),  the results showed that in the side-by-side condition children tended to be more indulgent with the robot's mistakes and to give it better feedback.
These results will allow us to take into account the variability of the judgement of the children relatively to the robot's performances.
\end{abstract}
